%-------------------------
% Resume in Latex - Rohan Singh Negi
% Based off of: https://github.com/jakegut/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Rohan Singh Negi} \\ \vspace{1pt}
    \small rohansinghnegi97@gmail.com $|$ 6399774044 $|$ Badowala, Dehradun \\
    % Add your LinkedIn and GitHub links below if you have them
    % \href{https://linkedin.com/in/yourprofile}{\underline{linkedin.com/in/yourprofile}} $|$
    % \href{https://github.com/yourusername}{\underline{github.com/yourusername}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Dehradun, India}
      {Bachelor Of Technology, Computer Science Engineering}{Aug. 2020 -- Aug. 2024}
      \resumeItemListStart
        \resumeItem{CGPA: 7.87/10}
      \resumeItemListEnd

    \resumeSubheading
      {Kendriya Vidyalaya IMA, Dehradun}{Dehradun, India}
      {Intermediate / 12th}{Mar. 2019 -- Mar. 2020}
      \resumeItemListStart
        \resumeItem{Percentage: 93\%}
      \resumeItemListEnd

    \resumeSubheading
      {Kendriya Vidyalaya IMA, Dehradun}{Dehradun, India}
      {High School / 10th}{Mar. 2017 -- Mar. 2018}
      \resumeItemListStart
        \resumeItem{Percentage: 88\%}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{LearnMate-agent} $|$ \emph{LangGraph, ReAct, Granite-3-3-8b, IBM watsonx Agent Lab}}{July 2025 -- Aug. 2025}
      \resumeItemListStart
        \resumeItem{Developed an intelligent agent to generate personalized course pathways using user interests, skill levels, and content preferences.}
        \resumeItem{Implemented interest-based filtering, skill-level adaptation, and goal-driven planning for structured learning.}
        \resumeItem{Leveraged LangGraph for dynamic workflows, ReAct for interactive decision-making, and integrated IBM watsonx Agent Lab for deployment.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Library Management System}}{Aug. 2023 -- Mar. 2024}
      \resumeItemListStart
        \resumeItem{Designed a relational database schema for managing book inventories, user accounts, and transaction records.}
        \resumeItem{Implemented CRUD operations for efficient data management using SQL, enhancing user experience and system efficiency.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Blockchain Based E-Voting System}}{Dec. 2022 -- Jun. 2023}
      \resumeItemListStart
        \resumeItem{Designed and deployed a secure and transparent e-voting system on the Ethereum blockchain ensuring tamper proof voting and smart contracts.}
        \resumeItem{Developed and tested smart contracts with Solidity in Remix IDE.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages:} Python, C, C++, Solidity, JavaScript, SQL, HTML, CSS \\
      \textbf{Frameworks/Tools:} LangGraph, ReAct, Granite-3-3-8b, IBM watsonx Agent Lab, Remix IDE \\
      \textbf{Database:} SQL \\
      \textbf{Other:} Cloud, Git, REST API
    }}
  \end{itemize}

%-----------SOFT SKILLS-----------
\section{Soft Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Problem Solving}, \textbf{Critical Thinking}, \textbf{Teamwork}, \textbf{Adaptability}, \textbf{Effective Communication}, \textbf{Time Management}, \textbf{Self-learning}, \textbf{Attention to Detail}
    }}
  \end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Introduction to Cybersecurity} --- Cisco Networking Academy\\
    Certificate: \href{https://github.com/Ron41202/certifications/blob/995d03deba715d88af29c97352229ceed320ee50/certificates/Introduction_to_Cybersecurity_certificate_rohannegi688-gmail-com_209484cb-60af-4207-b921-43918b5cc77e.pdf}{View PDF}
    \item \textbf{Journey to Cloud: Envisioning Your Solution} --- IBM SkillsBuild\\
    Certificate: \href{https://github.com/Ron41202/certifications/blob/995d03deba715d88af29c97352229ceed320ee50/certificates/IBMDesign20250803-31-hqkzt.pdf}{View PDF}
    \item \textbf{Getting Started with Artificial Intelligence} --- IBM SkillsBuild\\
    Certificate: \href{https://github.com/Ron41202/certifications/blob/995d03deba715d88af29c97352229ceed320ee50/certificates/IBMDesign20250803-29-s06v8q.pdf}{View PDF}
  \end{itemize}

%-------------------------------------------
\end{document}
